Decentralised Authoring, Annotations and Notifications for a Read-Write Web with dokieli

### 2017-04-07 index.tex
fine-tuning figure width
removed email of non-author
deleted word

\author{Sarven Capadisli\inst{1}
  \and Amy Guy\inst{2}
  \and Ruben Verborgh\inst{3}
  \and Christoph Lange\inst{1,4}
  \and Sören Auer\inst{1,4}
  \and Tim Berners-Lee\inst{5}}
\institute{%
  University of Bonn, Bonn, DE
  \email{info@csarven.ca, \{langec,auer\}@cs.uni-bonn.de}
  \and School of Informatics, University of Edinburgh, Edinburgh, UK
  \email{amy@rhiaro.co.uk}
  \and Ghent University – \empty imec, Ghent, BE
  \email{ruben.verborgh@ugent.be}
  \and Fraunhofer IAIS, Sankt Augustin, DE
  \and Decentralized Information Group, CSAIL, MIT, Cambridge, US
  \email{deiu@mit.edu, timbl@w3.org}
}
\maketitle

\begin{abstract}
  While the Web was designed as a decentralised environment, individual authors still lack the ability to conveniently author and publish documents, and to engage in social interactions with documents of others in a truly decentralised fashion. We present \textit{dokieli}, a fully decentralised, browser-based authoring and annotation platform with built-in support for social interactions, through which people retain the ownership of and sovereignty over their data. The resulting “living” documents are interoperable and independent of dokieli since they follow standards and best practices, such as HTML+RDFa for a fine-grained semantic structure, Linked Data Platform for personal data storage, and Linked Data Notifications for updates. This article describes dokieli’s architecture and implementation, demonstrating advanced document authoring and interaction without a single point of control. Such an environment provides the right technological conditions for independent publication of scientific articles, news, and other works that benefit from diverse voices and open interactions. To experience the described features please open this document in your Web browser under its canonical URI: {\tt \href{http://csarven.ca/dokieli-rww}{http://csarven.ca/dokieli-rww}}.
  \keywords{Decentralisation, Human-computer interaction, Linked Data, Semantic publishing, Social machine, Social web}
\end{abstract}

@@

\begin{figure}
  \begin{minipage}[b]{.49\textwidth}
    \includegraphics[width=\textwidth]{media/images/dokieli-citation}
    \caption{Semantic inline citations in dokieli}
    \label{fig:dokieli-citation}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{.49\textwidth}
    \includegraphics[width=\textwidth]{media/images/dokieli-sparqlines}
    \caption{Sparqlines interaction in dokieli}
    \label{fig:dokieli-sparqlines}
  \end{minipage}
\end{figure}

>>>>

\author{Sarven Capadisli\inst{1}
  \and Amy Guy\inst{2}
  \and Ruben Verborgh\inst{3}
  \and Christoph Lange\inst{1,4}
  \and Sören Auer\inst{1,4}
  \and Tim Berners-Lee\inst{5}}
\institute{%
  University of Bonn, Bonn, DE
  \email{info@csarven.ca, \{langec,auer\}@cs.uni-bonn.de}
  \and School of Informatics, University of Edinburgh, Edinburgh, UK
  \email{amy@rhiaro.co.uk}
  \and Ghent University – \empty imec, Ghent, BE
  \email{ruben.verborgh@ugent.be}
  \and Fraunhofer IAIS, Sankt Augustin, DE
  \and Decentralized Information Group, CSAIL, MIT, Cambridge, US
  \email{timbl@w3.org}
}
\maketitle

\begin{abstract}
  While the Web was designed as a decentralised environment, individual authors still lack the ability to conveniently author and publish documents, and to engage in social interactions with documents of others in a truly decentralised fashion. We present \textit{dokieli}, a fully decentralised, browser-based authoring and annotation platform with built-in support for social interactions, through which people retain ownership of and sovereignty over their data. The resulting “living” documents are interoperable and independent of dokieli since they follow standards and best practices, such as HTML+RDFa for a fine-grained semantic structure, Linked Data Platform for personal data storage, and Linked Data Notifications for updates. This article describes dokieli’s architecture and implementation, demonstrating advanced document authoring and interaction without a single point of control. Such an environment provides the right technological conditions for independent publication of scientific articles, news, and other works that benefit from diverse voices and open interactions. To experience the described features please open this document in your Web browser under its canonical URI: {\tt \href{http://csarven.ca/dokieli-rww}{http://csarven.ca/dokieli-rww}}.
  \keywords{Decentralisation, Human-computer interaction, Linked Data, Semantic publishing, Social machine, Social web}
\end{abstract}

@@

\begin{figure}
  \begin{minipage}[b]{.53\textwidth}
    \includegraphics[width=\textwidth]{media/images/dokieli-citation}
    \caption{Semantic inline citations in dokieli}
    \label{fig:dokieli-citation}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{.45\textwidth}
    \includegraphics[width=\textwidth]{media/images/dokieli-sparqlines}
    \caption{Sparqlines interaction in dokieli}
    \label{fig:dokieli-sparqlines}
  \end{minipage}
\end{figure}
